Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-28 paper/paper.tex
added captions to paper, added scale bar to plot-arrow-ave Tested everything on quipu.

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/paper-arrow-plot}
%%   \caption{Arrow plots for our simulation and mannik's experimental}
%%   \label{arrow-compare-mannik}
%% \end{figure}

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied movies that show the change in concentration
of MinD over time We have found that the deterministic simulations of
the protein reaction sequence discussed above results in robust
oscillatory behavoir of polar selection and oscillation in a wide
variety of cell shapes.  This differs with Mannik's experimental
findings that show much less regular behavoir, with a large variation
in the location of maxima.  On the other hand, our stochastic
simulations show irregular behavoir in the irregular shapes and more
regular, pole to pole oscillations in the pill and stadium shaped
cells.

Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
simulated with the stochastic method and with the deterministic
method, along with a plot taken from Mannik showing the location of
sequential MinD maxima in the experimental cells.  Like Manniks, the
tips of the arrows in our plots show subsequent maxima, and the data
overlays a color plot of time averaged MinD concentration.  These
plots illustrate the adequacy of the stochastic method and inadequacy
of the deterministic one.  The stochastic plots show similar random behavoir to Manniks

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrow plots of our pill shape}
  \label{pill-arrow}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
  \caption{box plots of Mannik's shapes}
  \label{box-mannik}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
  \caption{box plots of stadium shape}
  \label{box-stadium}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
  \caption{Arrow plots of our randst shape}
  \label{randst-plot-ave}
\end{figure}

>>>>

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied different plots and movies that show the
change in concentration of MinD over time We have found that the
deterministic simulations of the protein reaction sequence discussed
above results in robust oscillatory behavoir of polar selection and
oscillation in a wide variety of cell shapes.  This differs with
Mannik's experimental findings that show much less regular behavoir,
with a large variation in the location of maxima.  On the other hand,
our stochastic simulations show irregular behavoir in the irregular
shapes and more regular, pole to pole oscillations in the pill and
stadium shaped cells.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD density.
    At this point the data is over varying amounts of time but its all
    roughly 1000 seconds\fixme{fix this}.  The top row shows plots
    published by Mannik of the MinD maxima behavoir and the bottom two
    rows show our pancake shapes that are designed to have the same
    shape.  The middle row shows results from the stochastic
    simulation and the bottom shows results from the deterministic.
    We can see that the stochastic method shows behavoir that is
    similar to experiment while the deterministic method shows
    maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure}

Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
simulated with the stochastic method and with the deterministic
method, along with a plot taken from Mannik showing the location of
sequential MinD maxima in the experimental cells.  Like Mannik's, the
tips of the arrows in our plots show subsequent maxima, and the data
overlays a color plot of time averaged MinD concentration.  These
plots illustrate the adequacy of the stochastic method and inadequacy
of the deterministic one.  The stochastic plots show similar random behavoir to Manniks

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD
    density.\fixme{how much of time of data is shown?}.  Although
    there is variation in the specific location of maxima on each edge
    of the cell, the behavoir for both of these regular shapes is
    robust and exhibits a back and forth oscillatory manner.  The
    wildtype pill shape behavoir matches well with experiment.
    Regular pancake shapes have not been observed experimentally, but
    our stochastic simulations would suggest that they would exhibit
    regular robust oscillations similar to the pill shapes.  This is
    in contrast to the behavoir of Mannik cells seen in
    Figure~{randst-plot-ave}}
  \label{arrow-pill-stadium}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show a disparity between
    the behavoir of the stochastic and deterministic simulations in
    our Mannik cells.  The deterministic show a regular, robust
    oscillatory behavoir between the two ends of the cell. The
    stochastic simulation do show a general back and forth tendency
    between two ends of the cell, but it is not robust and tends to
    break down.}
  \label{box-mannik}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show the similarity
    between the stadium shapes simulated stochastically and
    deterministically.  Both show regular oscillatory maxima with
    similar periods.  This is in contrast to our boxpplot comparison
    of one of the Mannik shapes in Figure~\ref{box-mannik}}
  \label{box-stadium}
\end{figure}
